---
title: "Group Project (Fast Campus)"
author: "Jiwon Kim"
date: '2018-08-06'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(leaflet)
library(dplyr)
library(ggplot2)
library(lubridate)
library(anytime)
library(timeDate)
library(stringr)
library(readxl)
library(funModeling)
library(tidyr)
library(data.table)
```

# 서울시 공공자전거

#### Airbnb, Uber 등과 같은 공유경제모델 색깔을 띈 회사들이 많이 나와 국민들의 관심 또한 커져 범정부적 차원에서도 공공 welfare를 위한 많은 프로그램들이 나왔다. 
<br> 

#### 예를들면 서울시 정부차원에서 만든 

# 종속변수
# Count: 
<br> 

# 독립변수: 
# Weekend: 
# time.1 :
# time.2:
# time.3:
# time.4:
# time.5: 
# temperature : 
# precipitation: 
# windspeed: 
# humidity: 
# visibility: 
# ozone: 
# pm10: 
# pm2.5: 





When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
